A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-01-28 paper.tex
Add Gilles comments

\newcommand\ignore[1]{}
\newcommand{\imagepathext}[5]{%
\begin{figure}[hbtp]
\hfil\includegraphics[#1]{#2/#3.#4}\hfil
\caption{#5\label{#3}}
\end{figure}}

@@

We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].

@@

\subsection{Gestures taxonomies}
By looking in the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities so there is a need for a taxonomy.
Many possible taxonomies exist according to the technical or analytical aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}
%Gesture and Thoughts, page 18
\begin{description}
 \item[Gesticulation] is motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

We have chosen to analyze gesticulations as they are the most frequent.
%, and project them on the technical taxonomies.
And we have also made our own extraction from Talk-Shows.

%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive

@@

@@

We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
%We have tried to target the following kinds of gestures in a first step.

The figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and in the end a cursor movement mode.

@@

\section{Technical Work}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}

\subsection{Used Materials}
We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\textbf{Space} & BGR & HSV & YCrCb & CIE Lab\\
  & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
  & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & &
\end{tabular}
\end{center}

@@

\subsection{Blob Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper. 
\ignore{
When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.
}
To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

@@

-- add screenshot of the work --

@@

\section{}

>>>>

\newcommand\ignore[1]{}
\newcommand{\imagepathext}[5]{%
\begin{figure}[!htbp]
\hfil\includegraphics[#1]{#2/#3.#4}\hfil
\caption{#5\label{#3}}
\end{figure}}

@@

We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
One major scenario why we rely on corresponds to educational games here a pupil
could control his/her avatar in a program led by a ``real'' TV animator.
This kind of scenarios needs to be able to manage commands interaction
like pointing, selecting and moving as well as natural gesture animation.

@@

\subsection{Gestures taxonomies}
By looking in the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities so there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
In order to describe and analyse each gesture, we can rely on the following
aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures:
\begin{description}
 \item[Gesticulation] is motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

In our work, we focalize on emblems commands and gesticulations.
%We have chosen to analyze gesticulations as they are the most frequent.
%, and project them on the technical taxonomies.
%And we have also made our own extraction from Talk-Shows.
%Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive

@@

In order to identify relevant gestures we have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
%We have tried to target the following kinds of gestures in a first step.

@@

The figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and in the end a cursor movement mode.
\pagebreak 
We have selected to support 4 basic gestures to be extended depending on the
context fulfilling the requirements of a benchmark scenario.

@@

\section{Technical Work}

Pipeline of the work:

\png{pipeline}{Pipeline of work components}

\subsection{Used Materials}
We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
This camera costs about 40\$ which is a reasonable price for a potential market deployment.

@@

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Space} & BGR & HSV & YCrCb & CIE Lab\\
\hline
 & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
 & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & & \\
\hline
\end{tabular}
\end{center}

@@

\subsection{Blobs Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper. 
\ignore{
When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.
}
To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

@@

-- add screenshot of the work --
%\pngl{point}{simplify}{List of modes}

\begin{figure}[!htb]
\centering
  \includegraphics[width=0.45\textwidth]{./pics/point.png}
  \includegraphics[width=0.4\textwidth]{./pics/simplify.png}
  \caption{List of modes}
%  \label{fig:Gestes}
\end{figure}

@@

\section{System integration of this interaction and future work}
--

Gesture + facial recog.
Voice recognition
Haptic 
--
